### 2019-10-01 uiuc.tex
adds mohaghegh image

\subsubsection{Accessibility and Accomodation}
 Many hotels are located around downtown Champaign and the Eastern 
 side of campus, making transportation easy. Champaign-Urbana Mass Transit 
 (CU-MTD) is a reliable public transportation service that sees millions of 
 riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
 can be paid in cash or using the Token Transit app. Additionally, an all-day 
 pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
 from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
 rideshare services are also plentiful.
 Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
airports, ground transportation to the Champaign area will be required. To this
end, Peoria Charter is a popular bus service with several 
daily trips between the UIUC campus and the Chicagoland area.

@@

The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering. It also engages in education and outreach programs to teach members of the surrounding community about nuclear science. One of our most popular outreach programs is Engineering Open House (EOH), during which ANS-UIUC repeatedly earns awards for best presentation of a society. EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research. Membership is currently around 70-80 students and has been steadily growing. The chapter works to host events catering to nuclear, plasma, and radiological concentrations. Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC. Professional development activities range from tours of various facilities to pizza with campus visitors. Some of the past tours have included Clinton Power Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.

@@

\subsubsection{Reliability and Risk Analysis}
Risk analysis represents the pinnacle of interdisciplinary research and education. Following the Three Mile Island disaster in 1979, Probabilistic Risk Assessment (PRA) has become a key pillar of the risk-informed nuclear regulatory framework, and is now a requirement for every nuclear power plant in the United States. Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA. It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks emerging from the interface of social and technical systems.

>>>>

\subsubsection{Accessibility and Accomodation}
 Many hotels are located around downtown Champaign and the Eastern 
 side of campus, making transportation easy. Champaign-Urbana Mass Transit 
 (CU-MTD) is a reliable public transportation service that sees millions of 
 riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
 can be paid in cash or using the Token Transit app. Additionally, an all-day 
 pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
 from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
 rideshare services are also plentiful.
 Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
airports, ground transportation to the Champaign area will be required. 
If flying into Chicago (ORD or MDW), attendees may choose to rent a car or take a bus to 
Champaign. The organizers recommend Peoria Charter in this case. Peoria Charter 
is a reliable bus company that offers several shuttles throughout the day from 
Chicago to the university. The Altgeld Hall Peoria bus stop is less than one block 
from the Illini Union and the TownePlace Suites.

@@

The ANS-UIUC maintains and develops a cohesive community of students in nuclear 
engineering. It also engages in education and outreach programs to teach 
members of the surrounding community about nuclear science. One of our most 
popular outreach programs is Engineering Open House (EOH), during which 
ANS-UIUC repeatedly earns awards for best presentation of a society. EOH is an 
annual event where members of the local community, from young children to 
senior adults, visit the engineering campus to learn more about STEM research. 
Membership is currently around 70-80 students and has been steadily growing. 
The chapter works to host events catering to nuclear, plasma, and radiological 
concentrations. Professional development plays a crucial role in student 
development, and it is the biggest part of member involvement at UIUC. 
Professional development activities range from tours of various facilities to 
pizza with campus visitors. Some of the past tours have included Clinton Power 
Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National 
Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. 
ANS-UIUC has historically been one of the best represented institutions at the 
annual student conference and hosting it is a tradition this chapter is eager 
to uphold.

@@

\subsubsection{Reliability and Risk Analysis}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{mohaghegh.jpg}
    \caption{Prof. Zahra Mohaghegh is an Assistant Professor in Nuclear, 
          Plasma, and Radiological Engineering and director of the 
          Socio-Technical Risk Analysis (SoTeRiA) Research Laboratory.}
  \end{center}
\end{wrapfigure}
Risk analysis represents the pinnacle of interdisciplinary research and education. Following the Three Mile Island disaster in 1979, Probabilistic Risk Assessment (PRA) has become a key pillar of the risk-informed nuclear regulatory framework, and is now a requirement for every nuclear power plant in the United States. Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA. It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks emerging from the interface of social and technical systems.
